Ethereum: A Secure Decentralised Compute Platform

### 2014-04-02 Paper.tex
Begin work on formal, non-sequential definition of execution model.

In addition to the system state $\mathbb{S}$, there are several pieces of important, immutable, information used in the execution environment that the execution agent must provide:

\begin{itemize}
\item $a$, the address of the account which own the code that is executing.
\item $o$, the sender address of the transaction that originated this execution.
\item $p$, the price of gas in the transaction that originated this execution.
\item $D$, the byte array that is the input data to this execution; if the execution agent is a transaction, this would be the transaction data.
\item $s$, the address of the account which caused the code to be executing; if the execution agent is a transaction, this would be the transaction sender.
\item $v$, the value passed to this account as part of the same procedure as execution; if the execution agent is a transaction, this would be the transaction value.
\item $H$, the block header of the previous block.
\item $H'$, the block header of the current block.
\item $n$, the block number of the current block.
\end{itemize}

The execution model defines the function $X$, which can compute the resultant state $\mathbb{S}'$, given the required information:

\begin{equation}
\mathbb{S}' \equiv X(\mathbb{S}, a, o, p, D, s, v, H, H', n)
\end{equation}

@@

>>>>

In addition to the system state $\mathbb{S}$, and the remaining gas for computation $g$, there are several pieces of important information used in the execution environment that the execution agent must provide:

\begin{itemize}
\item $a$, the address of the account which owns the code that is executing.
\item $o$, the sender address of the transaction that originated this execution.
\item $p$, the price of gas in the transaction that originated this execution.
\item $D$, the byte array that is the input data to this execution; if the execution agent is a transaction, this would be the transaction data.
\item $s$, the address of the account which caused the code to be executing; if the execution agent is a transaction, this would be the transaction sender.
\item $v$, the value passed to this account as part of the same procedure as execution; if the execution agent is a transaction, this would be the transaction value.
\item $H$, the block header of the previous block.
\item $H'$, the block header of the current block.
\item $n$, the block number of the current block.
\end{itemize}

These are assumed to be defined as such throughout. The execution model defines the function $X$, which can compute the resultant state $\mathbb{S}'$ and the remaining gas $g'$, given these definitions:

\begin{equation}
(\mathbb{S}', g') \equiv \Xi(\mathbb{S}, g)
\end{equation}

@@

\begin{eqnarray}
\Xi(\mathbb{S}, g) & \equiv & X(\mathbb{S}, \mathbb{M}) \\
\mathbb{M}_g & \equiv & g \\
\mathbb{M}_P & \equiv & 0 \\
\mathbb{M}_M & \equiv & [0, 0,...] \\
\mathbb{M}_i & \equiv & -1 \\
\mathbb{M}_T & \equiv & [] \\
X(\mathbb{S}, \mathbb{M}) & \equiv & \begin{cases}
(\mathbb{S}, \mathbb{M}) & \text{if} \quad term(\mathbb{S}, \mathbb{M})\\
X(O(\mathbb{S}, \mathbb{M})) & \text{otherwise}\\
\end{cases}
\end{eqnarray}
